The Astropy Project

### 2017-12-14 author.tex
collaborations and started necommands

\author[0000-0003-0872-7098]{A. M. Price-Whelan}
\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}

@@

\author[0000-0003-4243-2840]{H. M. G\"{u}nther}
\affiliation{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research, 70 Vassar St., Cambridge, MA 02139, USA}

\author[0000-0003-0079-4114]{P. L. Lim}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

@@

@@

\author[0000-0002-1821-0650]{K. L. Cruz}
\affiliation{Department of Physics and Astronomy, Hunter College, City University of New York, 695 Park Avenue, New York, NY 10065}
\affiliation{Physics, Graduate Center of the City University of New York, New York, NY, USA}
\affiliation{ Department of Astrophysics, American Museum of Natural History, New York, NY, USA}

@@

>>>>

\newcommand{\affilprinceton}{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
\newcommand{\affilmit}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research, 70 Vassar St., Cambridge, MA 02139, USA}
\newcommand{\affilstsci}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\collaboration{Primary paper contributors:}

\author[0000-0003-0872-7098]{A. M. Price-Whelan}
\affiliation{\affilprinceton}

@@

\author[0000-0003-4243-2840]{H. M. G\"{u}nther}
\affiliation{\affilmit}

\author[0000-0003-0079-4114]{P. L. Lim}
\affiliation{\affilstsci}

@@

\collaboration{Astropy coordination committee:}

@@

\author[0000-0002-1821-0650]{K. L. Cruz}
\affiliation{Department of Physics and Astronomy, Hunter College, City University of New York, 695 Park Avenue, New York, NY 10065}
\affiliation{Physics, Graduate Center of the City University of New York, New York, NY, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}

@@

\collaboration{Astropy contributors:}
